% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
% \usepackage[T1]{fontenc}
% \usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Peter Denton}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
% \def\footerlink{http://www.owlnet.rice.edu/\textasciitilde pbd1/}
\def\footerlink{\null}

% The following metadata will show up in the PDF properties
\hypersetup{
colorlinks = true,
urlcolor = black,
pdfauthor = {\name},
pdfkeywords = {physics, mathematics},
pdftitle = {\name: Curriculum Vitae},
pdfsubject = {Curriculum Vitae},
pdfpagemode = UseNone
}

\geometry{
body={6.5in, 9.7in},
left=1.0in,
top=0.9in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
\begin{list}{}{
\setlength{\leftmargin}{1.5em}
}
}{
\end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.1in}

\begin{minipage}{0.45\linewidth}
138 Village at Vanderbilt\\
Nashville TN 37212
\end{minipage}
\begin{minipage}{0.45\linewidth}
\begin{tabular}{ll}
Phone: & (616) 450-0749\\
Email: & \href{mailto:peterbd1@gmail.com}{\tt peterbd1@gmail.com} \\
\end{tabular}
\end{minipage}
\subsection*{Education}
\begin{itemize}
\item Ph.D. Physics, Vanderbilt University (in progress).
\item B.S. Physics, Rice University, 2010.
\item B.A. Mathematics, Rice University, 2010.
% \item Introduction to accelerator physics, United States Particle Accelerator School, 2009.
% \item Multi-variable calculus, differential equations, Grand Rapids Community College, 2005-2006.
\end{itemize}
\subsection*{Honors and Awards}
\begin{itemize}
\item Division of Particles \& Fields travel grant to the APS April 2013 meeting.
\item The Robert T. Lagemann Award for highest academic achievement by a first-year graduate student.
\item ``Topping-up" McMinn Fellowship.
\end{itemize}
\subsection*{Employment}
\begin{itemize}
\item DOE funded RA with Dr. Weiler at Vanderbilt University, Spring 2011--Present.
\item TA at Vanderbilt University, Fall 2010--Fall 2012.
\item RA with Dr. Pantelides at Vanderbilt University, Summer--Fall 2010.
\item Lee Teng Internship at Fermilab with Dr. Sen, Summer 2009.
\item TA for the Physics Department at Rice University, Fall 2009.
\item Bonner Labs at Rice University with Dr. Llope, Summer 2008.
\item Writing consultant at Rice University, 2007--2010.
% \item Grader for the Computational and Applied Mathematics department at Rice University, 2007--2008.
\end{itemize}
\subsection*{Research}
Dr. Tom Weiler
\begin{itemize}
\item The possibility of cosmic rays producing black holes in the atmosphere.
\item Cosmic ray anisotropy at the highest energies as seen through Pierre Auger Observator and JEM-EUSO.
% \item Neutrino mixing and sources.
\item Beyond the standard model contribution to dispersion integrals for $pp$ scattering at LHC energies.
\end{itemize}
Dr. Sokrates Pantelides
\begin{itemize}
\item DFT calculations of radiation effects of graphene.
\end{itemize}
Dr. Marj Corcoran
\begin{itemize}
\item Monte Carlo simulations looking for $CP$ violation in $WW\gamma$ decays.
\end{itemize}
Hulet Atom Cooling Group with Dr. Randy Hulet
\begin{itemize}
\item Design and construction of improved laser stabilization electronics.
\end{itemize}
Fermilab with Dr. Tanaji Sen
\begin{itemize}
\item Work on reconstructing the longitudinal phase space in the Main Injector and the Recycler.
% \item Work on the Vlasov code base.
\end{itemize}
Bonner Labs with Dr. Bill Llope
\begin{itemize}
\item Testing and designing components for TOF for STAR at BNL.
\item Confirming the long term accuracy of the calibration of electronics boards.
\item Testing various improvements of PMT's.
\end{itemize}
\subsection*{Language Skills}
\LaTeX, beamer, python, matplotlib, C++, ROOT, MATHEMATICA, MATLAB, FORTRAN, gnuplot, java, html, and javascript.
\subsection*{Teaching}
\begin{itemize}
\item English, math, and physics at middle school, high school, undergraduate, and graduate school levels.
% \item Grading and running help sessions for various physics courses.
\item Teaching assistant for various freshman physics labs.
\end{itemize}
\section*{Professional Societies}
\begin{itemize}
\item Member, American Physical Society
\end{itemize}
% \subsection*{Graduate Courses Taken}
% Mathematical methods, orders of magnitude, classical mechanics, statistical mechanics, advanced electrodynamics I \& II, quantum
% mechanics I \& II, particle physics, QFT I, GR. To be completed: QFT II, cosmology.

% \vspace*{.1in}
% Footer
% \begin{center}
% \begin{footnotesize}
% Updated: \today \\
% \href{\footerlink}{\texttt{\footerlink}}
% \end{footnotesize}
% \end{center}
\end{document}